---
title: 'Week 3 Assignment - Stars!'
author: "Martin Halwachs"
date: "1 August 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## slide
```{r, warning=FALSE, message=FALSE}
library(plotly)
makeStars <- setClass("stars",
                     slots=c(xPos="numeric",
                             yPos="numeric"))
setMethod(f="plot",
          signature="stars",
          definition=function(x,y,...) {
            radius <- if(length(x@xPos)>1)
              mean(sd(x@xPos), sd(x@yPos))/10
            else
              1
            xp <- matrix(ncol=length(x@xPos), nrow=11, 0)
            yp <- matrix(ncol=length(x@xPos), nrow=11, 0)
            for(i in 1:length(x@xPos))
            {
              outer.circle.x <- x@xPos[i] + radius * cos(pi/2 + c(1:5)*(2*pi)/5)
              outer.circle.y <- x@yPos[i] + radius * sin(pi/2 + c(1:5)*(2*pi)/5)
              inner.circle.x <- x@xPos[i] + radius/2 * cos(3*pi/2 + c(4:5,1:3)*(2*pi)/5)
              inner.circle.y <- x@yPos[i] + radius/2 * sin(3*pi/2 + c(4:5,1:3)*(2*pi)/5)
              
              for(j in 1:5)
              {
                xp[2*j-1,i] <- outer.circle.x[j]
                xp[2*j,i] <- inner.circle.x[j]
                yp[2*j-1,i] <- outer.circle.y[j]
                yp[2*j,i] <- inner.circle.y[j]
              }
              xp[11,i] <- outer.circle.x[1]
              yp[11,i] <- outer.circle.y[1]
            }
            
            p <- plot_ly(mode="lines",type="scatter")
            for(i in 1:length(x@xPos))
            {
              p <- add_trace(p, x=xp[,i], y=yp[,i])
            }
            p <- layout(p, xaxis = list(range = c(min(xp,yp), max(xp,yp))),
                           yaxis = list(range = c(min(xp,yp), max(xp,yp))))
            p
          })
z <- makeStars(xPos=rnorm(10),yPos=rnorm(10))
plot(z)
```

## The full code
i needed to import `plotly` and also wanted to do it in a class ... of course, there are easier ways, but it was just to practice

### library and class
```{r, eval=FALSE, echo=TRUE}
library(plotly)
makeStars <- setClass("stars",
                     slots=c(xPos="numeric",
                             yPos="numeric"))
```

***
### 1st part of Method
```{r, eval=FALSE, echo=TRUE}
setMethod(f="plot",
          signature="stars",
          definition=function(x,y,...) {
  radius <- if(length(x@xPos)>1)
    mean(sd(x@xPos), sd(x@yPos))/10
  else
    1
  xp <- matrix(ncol=length(x@xPos), nrow=11, 0)
  yp <- matrix(ncol=length(x@xPos), nrow=11, 0)
```

***
### 2nd part of Method
```{r, eval=FALSE, echo=TRUE}
  for(i in 1:length(x@xPos))
  {
    outer.circle.x <- x@xPos[i] + radius * cos(pi/2 + c(1:5)*(2*pi)/5)
    outer.circle.y <- x@yPos[i] + radius * sin(pi/2 + c(1:5)*(2*pi)/5)
    inner.circle.x <- x@xPos[i] + radius/2 * cos(3*pi/2 + c(4:5,1:3)*(2*pi)/5)
    inner.circle.y <- x@yPos[i] + radius/2 * sin(3*pi/2 + c(4:5,1:3)*(2*pi)/5)
```

***
### 3rd part of Method
```{r, eval=FALSE, echo=TRUE}
    for(j in 1:5)
    {
      xp[2*j-1,i] <- outer.circle.x[j]
      xp[2*j,i] <- inner.circle.x[j]
      yp[2*j-1,i] <- outer.circle.y[j]
      yp[2*j,i] <- inner.circle.y[j]
    }
    xp[11,i] <- outer.circle.x[1]
    yp[11,i] <- outer.circle.y[1]
  }
```

***
### Final part of Method
```{r, eval=FALSE, echo=TRUE}
  p <- plot_ly(mode="lines",type="scatter")
  for(i in 1:length(x@xPos))
  {
    p <- add_trace(p, x=xp[,i], y=yp[,i])
  }
  p <- layout(p, xaxis = list(range = c(min(xp,yp), max(xp,yp))),
                 yaxis = list(range = c(min(xp,yp), max(xp,yp))))
  p
})
```

***
### The usage
```{r, eval=FALSE, echo=TRUE}
z <- makeStars(xPos=rnorm(10),yPos=rnorm(10))
plot(z)
```

## Notes
I had an initial problem in using `plotly`. I wanted to substitute this (first plot)
```{r,eval=FALSE, echo=TRUE}
df <- data.frame(x=c(1,2,3), y=c(2,4,5), y=c(4,1,3))
p <- plot_ly(mode="lines", type="scatter")
p <- add_trace(p, x=~df[,1], y=~df[,2])
p <- add_trace(p, x=~df[,1], y=~df[,3])
p
```
with this (second plot):
```{r,eval=FALSE, echo=TRUE}
df <- data.frame(x=c(1,2,3), y=c(2,4,5), y=c(4,1,3))
p <- plot_ly(mode="lines", type="scatter")
for(i in 2:3)
  p <- add_trace(p, x=~df[,1], y=~df[,i])
p
```

***
### First plot
```{r}
df <- data.frame(x=c(1,2,3), y=c(2,4,5), y=c(4,1,3))
p <- plot_ly(mode="lines", type="scatter")
p <- add_trace(p, x=~df[,1], y=~df[,2])
p <- add_trace(p, x=~df[,1], y=~df[,3])
p
```

***
### Second plot
```{r}
df <- data.frame(x=c(1,2,3), y=c(2,4,5), y=c(4,1,3))
p <- plot_ly(mode="lines", type="scatter")
for(i in 2:3)
  p <- add_trace(p, x=~df[,1], y=~df[,i])
p
```

## The solution (Code)
I found the solution, by asking on Stack Overflow [here](https://stackoverflow.com/questions/45448320/weird-behaviour-of-plot-ly-in-r-if-using-for-loop-to-create-dynamic-number-of-l/45448479?noredirect=1#comment77858331_45448479]), which was dismissing the tildes:
```{r, eval=FALSE, echo=TRUE}
df <- data.frame(x=c(1,2,3), y=c(2,4,5), y=c(4,1,3))
p <- plot_ly(mode="lines", type="scatter")
for(i in 2:3)
  p <- add_trace(p, x=df[,1], y=df[,i])
p
```
I still don't no why, but maybe this information is useful to you as well.

## The solution (Plot)
```{r}
df <- data.frame(x=c(1,2,3), y=c(2,4,5), y=c(4,1,3))
p <- plot_ly(mode="lines", type="scatter")
for(i in 2:3)
  p <- add_trace(p, x=df[,1], y=df[,i])
p
```

# Thank you
